\normalfont\spacedallcaps{Programmentwurf}

### 2022-04-21 Chess-AdvancedSE/Docs/Doku/newDoku/structure.tex
Renamed "Entitys" to "Entities" ;)
bissle gedokut

@@

@@

@@

%----------------------------------------------------------------------------------------
%	HYPERLINKS
%---------------------------------------------------------------------------------------

\hypersetup{
%draft, % Uncomment to remove all links (useful for printing in black and white)
colorlinks=true, breaklinks=true, bookmarks=true,bookmarksnumbered,
urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen, % Link colors
pdftitle={}, % PDF title
pdfauthor={\textcopyright}, % PDF Author
pdfsubject={}, % PDF Subject
pdfkeywords={}, % PDF Keywords
pdfcreator={pdfLaTeX}, % PDF Creator
pdfproducer={LaTeX with hyperref and ClassicThesis} % PDF producer
}

>>>>

\usepackage{hyperref}

\usepackage{csquotes}

@@

\usepackage{setspace}

@@

%---------------------------------------------------------
%   HYPERREF SETTINGS
%---------------------------------------------------------
\def\figureautorefname{Abbildung}
\def\sectionautorefname{Abschnitt}
\def\subsectionautorefname{Unterabschnitt}
\def\subsubsectionautorefname{Unterunterabschnitt}

@@
